New lower bounds for Schur and weak Schur numbers

### 2021-04-11 article/sat.tex
ajout des valeurs

\par
\cite{ELIAHOU2012175} verified with a SAT solver that there are no partition in 5 weakly sum-free subsets of
\([\![1,197]\!]\) with
\(A_5 = \{67, 68\} \cup [\![70,134]\!] \cup \{136\}\) in 17 hours and could not provide a similar result when only
assuming \(m_5 = 67\) even after several
weeks of runtime. By using the same method as above, we were able to verify that \(WS(5 | m_5 = 67) = 196\) in 0.5
seconds with the SAT solver glucose \cite{Glucose}
on a 2.60 GHz Intel i7 processor PC (we used the non-parallel version here for the sake of comparison but in the rest of
this subsection, we used the parallel version of glucose).
The additional information we gave to the SAT solver is that every partition of \([\![1,66]\!]\) in 4 weakly sum-free
subsets starts with a partition of
\([\![1,23]\!]\) in 3 weakly sum-free subsets (this can be checked in a few dozens of minutes with a SAT solver). Among
the 3 partitions of \([\![1,23]\!]\) in
3 weakly sum-free subsets, every number always appears in the same subset except for 16 and 17 which can appear in two
different subsets. We hardcoded
this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation
time. We also give the stronger following result.

\begin{computational theorem}
If there exists a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets then \(m_5 \leq\). NB : on doit finir d'obtenir les valeurs.
\end{computational theorem}

@@

\begin{tabular}{| c | *{21}{ p{2mm} |}}
	\hline
	\(m_4\) & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 & 23 & 24 \\
	\hline
	\(WS(4 | m_4) + 1\) & 55 & 59 & 60 & 59 & 59 & 60 & 60 & 60 & 60 & 64 & 63 & 64 & 61 & 64 & 63 & 65 & 65 & 65 & 65 & 66
	& 67 \\
	\hline
	\(max~m_5\) & 49 & 51 & 54 & 53 & 54 & 54 & & & & & & & & & & & & 59 & 61 & 58 & 53 \\
	\hline
\end{tabular}

In the above table, we only made real efforts (trying different additionnal information) for \(m_4 = 24\). In this case, the value \(m_5 \leqslant 53\) 
was obtained after 7 hours of runtime.
To obtain these results, we once again provided additionnal information to the SAT solver. We added two different types information. 
The first one is the same above. The second one is maximum length of a sequence using only a certain subset of the colors. For instance, 
if \(m_4 \geqslant 22\), then there cannot be more than 17 consecutive numbers with color 1, 2 or 3. \\

>>>>

\par
\cite{ELIAHOU2012175} verified with a SAT solver that there are no partition in 5 weakly sum-free subsets of
\([\![1,197]\!]\) with
\(A_5 = \{67, 68\} \cup [\![70,134]\!] \cup \{136\}\) in 17 hours and could not provide a similar result when only
assuming \(m_5 = 67\) even after several
weeks of runtime. By using the same method as above, we were able to verify that \(WS(5 | m_5 = 67) = 196\) in 0.5
seconds with the SAT solver glucose \cite{Glucose}
on a 2.60 GHz Intel i7 processor PC (we used the non-parallel version here for the sake of comparison but in the rest of
this subsection, we used the parallel version of glucose).
The additional information we gave to the SAT solver is that every partition of \([\![1,66]\!]\) in 4 weakly sum-free
subsets starts with a partition of
\([\![1,23]\!]\) in 3 weakly sum-free subsets (this can be checked in a few dozens of minutes with a SAT solver). Among
the 3 partitions of \([\![1,23]\!]\) in
3 weakly sum-free subsets, every number always appears in the same subset except for 16 and 17 which can appear in two
different subsets. We hardcoded
this external knowledge in the propositional formula which allowed us to gain several orders of magnitude in computation
time. Since \(WS(4) = 66\), we have \(m_5 \leqslant 67\). We give the stronger following result.

\begin{computational theorem}
If there exists a partition of \([\![1,197]\!]\) in 5 weakly sum-free subsets then \(m_5 \leqslant 59\).
\end{computational theorem}

@@

\renewcommand{\arraystretch}{1.5}
\setlength{\tabcolsep}{3pt}

\begin{center}
\begin{tabular}{| c | *{21}{c |}}
	\hline
	\(m_4\) & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 & 23 & 24 \\
	\hline
	\(WS(4 | m_4) + 1\) & 55 & 59 & 60 & 59 & 59 & 60 & 60 & 60 & 60 & 64 & 63 & 64 & 61 & 64 & 63 & 65 & 65 & 65 & 65 & 66
	& 67 \\
	\hline
	\(max~m_5\) & 49 & 51 & 54 & 53 & 54 & 54 & 55 & 55 & 55 & 55 & 55 & 56 & 57 & 57 & 59 & 59 & 59 & 59 & 59 & 58 & 53 \\
	\hline
\end{tabular}
\end{center}

For \(m_4 = 24\), the value \(m_5 \leqslant 53\) was obtained after 7 hours of runtime, and for  \(m_4 = 22\), the 
value \(m_5 \leqslant 59\) was obtained after 11 hours of runtime. All the other values took between 1 minutes and 2 hours.
To obtain these results, we once again provided additionnal information to the SAT solver. We added two different types information. 
The first one is the same as previously: we compute the subsets in which the first numbers can appear. The second type of 
information is the maximum length of a sequence using only a certain subset of the colors. For instance, 
if \(m_4 \geqslant 22\), then there cannot be more than 17 consecutive numbers with color 1, 2 or 3. \\
